Arterial pulsations cannot drive intramural periarterial drainage: Significance for \Ab drainage

### 2017-07-29 paper.tex
added injection location

\subsection{Perivascular Drainage through the MCA}

@@

Mice were anaesthesized with isoflurane, placed prone on a stereotaxic instrument and secured with head adaptors. Baseline measurements of oxygen saturation, heart rate, breath rate and pulse distension were taken before administering Ate. A volume of \SI{0.5}{\micro\litre} of \Ab$_{1-40}$ HiLyte Fluor 555 (Cambridge Bioscience, UK) was stereotaxically injected into the left hippocampus at a rate of \SI{0.2}{\micro\litre\per\minute}. Injection pipettes were left \textit{in situ} for \SI{2}{\minute} to prevent reflux. Mice were euthanized \SI{5}{\minute} after withdrawal of the injection pipette through overdose with pento-barbital (\SI{200}{\milli\gram\per\kilo\gram}). Mice were then intracardially perfused with \SI{0.01}{\Molar} phosphate buffered saline (PBS), pH 7.2 followed by \SI{4}{\percent} paraformaldehyde in \SI{0.01}{\Molar} PBS, pH 7.2. Brains were removed, post fixed overnight in fresh fixative and then processed for immunohistochemistry and image analysis. For controls, ten week old wild-type C57B16 mice were processed following the same method, but without the administration of Ate ($n = 3$). Detailed materials and methods can be found in SI~3.

>>>>

\subsection{IPAD through the MCA}

@@

Mice were anaesthesized with isoflurane, placed prone on a stereotaxic instrument and secured with head adaptors. Baseline measurements of oxygen saturation, heart rate, breath rate and pulse distension were taken before administering Ate. A volume of \SI{0.5}{\micro\litre} of \Ab$_{1-40}$ HiLyte Fluor 555 (Cambridge Bioscience, UK) was stereotaxically injected into the left hippocampus at a rate of \SI{0.2}{\micro\litre\per\minute} (coordinates from Bregma: AP = \SI{-1.9}{\mm}; ML = \SI{1.5}{\mm} and DV = \SI{-1.7}{\mm}). Injection pipettes were left \textit{in situ} for \SI{2}{\minute} to prevent reflux. Mice were euthanized \SI{5}{\minute} after withdrawal of the injection pipette through overdose with pento-barbital (\SI{200}{\milli\gram\per\kilo\gram}). Mice were then intracardially perfused with \SI{0.01}{\Molar} phosphate buffered saline (PBS), pH 7.2 followed by \SI{4}{\percent} paraformaldehyde in \SI{0.01}{\Molar} PBS, pH 7.2. Brains were removed, post fixed overnight in fresh fixative and then processed for immunohistochemistry and image analysis. For controls, ten week old wild-type C57B16 mice were processed following the same method, but without the administration of Ate ($n = 3$). Detailed materials and methods can be found in SI~3.
